---
title: "Intonation & Memory: Data preparation"
author: "Michelina Savino, Martine Grice, Bodo Winter"
date: "7/16/2018"
output: html_document
---

```{r knitr_setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

This script uses "recall_cleaned.csv" from the "preprocessing.Rmd" to compute descriptive stats of the data.

## Preprocessing

We begin by loading in the packages and data:

```{r setup, warning = FALSE, message = FALSE}
# Load packages:

library(tidyverse)
library(scales)

# Load data:

recall <- read_csv('../data/recall_cleaned.csv')
```

## Descriptive stats:

What is the average accuracy per condition?

```{r}
cond_avgs <- recall %>% group_by(Condition) %>% 
  summarize(ACC = mean(ACC)) %>% 
  mutate(ACC = round(ACC, 3),
         percentage = str_c(ACC * 100, '%'))
cond_avgs
write_csv(cond_avgs, '../data/condition_averages.csv')
```

What is the average accuracy per modality?

```{r}
mod_avgs <- recall %>% group_by(Modality) %>% 
  summarize(ACC = mean(ACC)) %>% 
  mutate(ACC = round(ACC, 3),
         percentage = str_c(ACC * 100, '%'))
mod_avgs
write_csv(mod_avgs, '../data/modality_averages.csv')
```

What is the average accuracy per condition & triplet?:

```{r}
trip_cond <- recall %>% group_by(Triplet, Condition) %>% 
  summarize(ACC = mean(ACC)) %>% 
  mutate(ACC = round(ACC, 3),
         percentage = str_c(ACC * 100, '%'))
trip_cond
write_csv(trip_cond, '../data/triplet_condition_averages.csv')
```

This completes this script.
