---
title: "Intonation & Memory: Data preparation"
author: "Michelina Savino, Martine Grice, Bodo Winter"
date: "7/16/2018"
output: html_document
---

```{r knitr_setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

This experiments investigates the effects of pauses and intonation in serial recall. Lists of 9 digits were presented in four conditions (within-subjects):

- C: control condition, which has monotone intonation and no pauses
- P: pause condition, which has monotone intonation with pauses
- A: intonation contour A, with non-final intonation boundaries on the 3rd and 6th digit
- B: intonation contour B, which is the same as A with additional penultimate pitch excursion on the penultimate position of each triplet (positions 2, 5 and 8)

In addition, there were three modality conditions, which refer to how participants performed the recall.

- oral recall
- written recall, keyboard
- written recall, grid with tripartite structure

This script gets the data in shape for the other scripts.

## Preprocessing

We begin by loading in the packages and data:

```{r setup, warning = FALSE, message = FALSE}
# Load packages:

library(tidyverse)
library(scales)

# Load data:

oral <- read_csv('../data/oral.csv')
grid <- read_csv('../data/grid.csv')
kboard <- read_csv('../data/keyboard.csv')

# Display one of them to show general structure:

head(oral)

```

This data is in wide format. The conditions are "C", "P", "A", and "B". Let's change the column names that have spaces and/or special characters in them to simpler column names:

```{r renaming, warning = FALSE}
oral <- rename(oral,
               Ppt = `PART#`,
               Age = `Age (yy)`,
               DigitSpan = `Digit span`,
               Modality = Rec_mod)
grid <- rename(grid,
               Ppt = `PART#`,
               Age = `Age (yy)`,
               DigitSpan = `Digit span`,
               Modality = Rec_mod)
kboard <- rename(kboard,
               Ppt = `PART#`,
               Age = `Age (yy)`,
               DigitSpan = `Digit span`,
               Modality = Rec_mod)
```

Let's now merge the three files into one:

```{r merging, warning = FALSE}
recall <- bind_rows(oral, grid, kboard)
```

Finally we can convert from wide to long format. As a result of this, the information C_01, C_02 etc. will be in one column "CondPos". This needs to be separated into the condition information (the letter preceding the "_") and position information (the number following the underscore).

```{r wide_to_long, warning = FALSE}
recall <- gather(recall,
                 key = 'CondPos',
                 value = 'Correct', C_01:P_09) %>% 
  separate(CondPos, into = c('Condition', 'Position'))
```

Participants have numerical identifiers that are repeated throughout the different between-subjects experimental conditions. We need to create unique subject identifiers so that we can later adequately deal with any possible violations of the independence assumptions.

```{r unique_IDs, warning = FALSE}
recall <- unite(recall, ID, Modality, Ppt, remove = FALSE)
```

We should make position into an integer variable, and we will also create a new column with accuracy data (percent correct).

```{r more_cleaning, warning = FALSE}
recall <- mutate(recall,
                 Position = as.numeric(Position),
                 ACC = Correct / 15)
```

Finally, let's arrange the data frame by participant and within participant, by condition and position.

```{r sorting, warning = FALSE}
recall <- arrange(recall,
                  ID, Condition, Position)
```

Relabel the Condition column in a more transparent fashion:

```{r}
mykey <- tibble(Condition = unique(recall$Condition),
                ConditionNew = c('Intonation A', 'Intonation B', 'Control', 'Pause'))
recall <- left_join(recall, mykey) %>%
  select(-Condition) %>%
  rename(Condition = ConditionNew)
```

Next, we will create special meanings for the the first, second and third variable for each triplet. Let's code this as a categorical factor with three distinct levels.

```{r special_positions, warning = FALSE}
recall$Triplet <- as.factor(1:3)
```

Center relevant variables:

```{r}
recall <- mutate(recall,
                 DigitSpan_c = DigitSpan - mean(DigitSpan))
```

Create a variable for ultimate versus non-ultimate:

```{r}
recall <- mutate(recall,
                 Ultimate = ifelse(Position %in% c(3, 6),
                                   'ultimate', 'not'))
```

Let's center the position variable and create a quadratic transform of it to capture any quadratic bends (as expected per primacy and recency effects).

```{r create_quadratics, warning = FALSE}
recall <- mutate(recall,
                 Pos_c = Position - mean(Position),
                 Pos_c2 = Pos_c ^ 2)
```

Write this data:

```{r}
write_csv(recall, '../data/recall_cleaned.csv')
```

This completes this script.
